\documentclass[../revisedmain.tex]{subfiles}
\begin{document}
	\begin{center}
		\Large{Exercises}
	\end{center}
	\begin{enumerate}
		\item \textbf{What would be the unit of:}
		\begin{enumerate}
			\item $f'(x)$ where $y=f(x)$ is in $y$ inches and $x$ seconds
			\item The second derivative of the area of a circle: $A=\pi r^2$ where $A$ is in square meters and $r$ is in linear meters
			\item The rate of change of acceleration of the function $x(t)=15t^2+15t+5$ where $x(t)$ is in meters and $t$ is in seconds
		\end{enumerate}
		\item \textbf{Find the value including correct units:}
		\begin{enumerate}
			\item $V''(5)$ where $V(r)=\frac{4}{3}\pi r^3$ with $V(r)$ in cubic meters and $r$ in linear meters
			\item The acceleration and veolcity of a model rocket at time $t=2$ seconds with the rocket's position is given by $x(t)=-4.9t^2+100t-2$ in meters
			\item The second derivative of $g(s)=s^2*\sin(s)$ where $g(s)$ is in dollars and $s$ is in quality units (abbreviated \textit{q})
		\end{enumerate}
		\item \textbf{Solve the problems and give correct units:}
		\begin{enumerate}
			\item Mr. Regina is a NASCAR driver and he recently got a new car, the \textit{Eyremobile}. Powered by high-quality literature, the \textit{Eyremobile} performs better than his previous racecar and its position, if run at full power, is given by the function: \[x(t)=\frac{t}{20}-\frac{3}{10}\ln(t+6)\] where $x(t)$ is measured in miles and $t$ is time in seconds.
			\begin{enumerate}
				\item Find the velocity equation for the \textit{Eyremobile} running at full power.
				\item If Mr. Regina exceeds 210 miles per hour on a curve, he will fly off the track. Will Mr. Regina be safe if he runs the \textit{Eyremobile} at full power over the 30 minute race? Give a sound explanation with evidence.
			\end{enumerate}
		\end{enumerate}
	\end{enumerate}
\end{document}