\documentclass[../revisedmain.tex]{subfiles}
\begin{document}
	\begin{enumerate}
		\item As with almost everything, the best way to succeed on the test is to study.
		\item Calculus builds off of itself. If you are lost or unsure about something, seek help.
		\item Do not give up. Calculus is hard for everybody.
		\item The College Board \textit{loves} to make the test confusing. Take as many practice tests as possible.
		\item When selecting answers, check to see if there are different ways to write your answer. For example, \(\sqrt{x}\) is the same as \(x^{.5}\). Check to make sure you have fully simplified, too.
		\item If you have extra time, check your work. If you have extra time beyond that, redo whatever problems you are not 100\% sure about.
		\item Doing homework is more important than ever. You should never, ever copy any one else's homework. A good grade on a homework assignment is not worth a bad score on quizzes, tests, or the AP test.
		\item If you are having extreme difficulty on a problem and cannot figure out how to complete it even after reviewing your notes and the textook(s), do not fake your way through it. Leave it unfinished and ask for help.
		\item Ask for help! Do not be afraid to ask. Your teacher is an exceptional (and most likely the best) resource. Other great resources include:
		\begin{enumerate}
			\item \textbf{Khan Academy} - good resource, can be a little slow moving at times
			\item \textbf{Wolfram MathWorld} - the best resource on the web, explanations can be too advanced or abstract occasionally
			\item \textbf{Stack Exchange} - often has the best explanations of problems but not all topics are asked about
		\end{enumerate}
		Some resources you may want to get a second opinion on are:
		\begin{enumerate}
			\item People who have passed AP Calculus
			\item Other online forums
			\item Other students in your class
		\end{enumerate}
	\end{enumerate}
\end{document}